\textsc{\wobble: a data-driven method for precision radial velocities}

### 2019-08-12 paper/paper.tex
overwriting with updated paper

\begin{figure*}
\centering
\includegraphics[width=5in]{telluric_basis2}
\caption{Example of the mean telluric spectral template in a small wavelength region (upper panel) and the three basis vectors used to capture the time-variable contributions to the spectrum, staggered by an arbitrary offset for display (lower panel).}
\label{fig:telluric_basis}
\end{figure*}

An example of the inferred variability from the 51 Peg analysis is shown in Figure \ref{fig:telluric_basis}. 
There is clearly coherent structure in the variations. 
As we might expect, many of the lines co-vary with each other: as all known telluric lines in this region arise from H$_2$O, this likely corresponds to time-variable levels of atmospheric water vapor content. 
In general, the basis vectors are suggestive of Doppler shifts, perhaps due to wind speeds in different layers of the atmosphere contributing individually to the overall line shapes. 
These hypotheses could be tested in the future by seeking correlations between basis weights and externally-measured weather diagnostics. 
%\todo{(is this enough? also show that basis weights change seasonally-ish?)}

>>>>

\begin{figure*}
\centering
\includegraphics[width=5in]{telluric_basis}
\caption{Example of the mean telluric spectral template in a small wavelength region (upper panel) and the three basis vectors used to capture the time-variable contributions to the spectrum, staggered by an arbitrary offset for display (lower panel).}
\label{fig:telluric_basis}
\end{figure*}

An example of the inferred variability from the 51 Peg analysis is shown in Figure \ref{fig:telluric_basis}. 
There is clearly coherent structure in the variations. 
As we might expect, many of the lines co-vary with each other: as all known telluric lines in this region arise from H$_2$O, this likely corresponds to time-variable levels of atmospheric water vapor content. 
\deleted{In general, the basis vectors are suggestive of Doppler shifts, perhaps due to wind speeds in different layers of the atmosphere contributing individually to the overall line shapes.} 
These hypotheses could be tested in the future by seeking correlations between basis weights and externally-measured weather diagnostics. 
%\todo{(is this enough? also show that basis weights change seasonally-ish?)}
